Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-10 demystify.tex
updates

\autoref{tab:us-vs-other} summarizes the main differences between CS PhD in the US and other countries. % This is based on my experience and what I heard from others who did PhD in other countries.

@@

In other countries, you often start your research right away, e.g., you immediately work on the research project you proposed with the adviser you chose. Moreover, you might not have exams like those in the US or only have to do a few of them.

\emph{Funding}:  In many countries, funding comes from the university or the gov't. This funding often has a fixed duration (e.g., 3 or 4 years).  In the US (\autoref{sec:funding}), funding (e.g., RA) comes directly from your adviser (no fixed duration).  There are also fewer TA opportunities in European universities compared to the US.

>>>>

\autoref{tab:us-vs-other} summarizes the main differences between CS PhD in the US and other countries. Note that these differences can vary by institution and country.  Some countries might have a PhD program that is similar to the US.  The following are some common differences:

@@

In other countries, you often start your research right away and work on the research project you proposed with the adviser you chose. Moreover, you might not have exams like those in the US or only have to do a few of them.

\emph{Funding}:  In many countries, funding comes from the university or the gov't. This funding often has a fixed duration, e.g., 3 or 4 years.  In the US (\autoref{sec:funding}), funding (e.g., RA) comes directly from your adviser (no fixed duration).  There are also fewer TA opportunities in European universities compared to the US.
